\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-27 pldi/draft.tex
A note on parallelism

\heading{A Note on the Parallelism Factor}
\nv{
The discussion of the benchmarks often refers to the parallelism factor 
This is not necessarily the resulting parallelism achieved by \sys, which typically is above the level configured by the user.
This is because for each process (node in the graph), \sys creates multiple processes---aggregators, splitters, relays \etc
Some times the results give the impression of superlinear parallelism, but this has a simple explanation.
}

>>>>

\heading{A Note on the Parallelism Factor}
%
The discussion of the results often mentions the parallelism factor, which refers to the \sys \emph{parallelism configuration} rather than the resulting parallelization. In fact, for small parallelism configurations \sys often achieves higher parallelization due to the creation of multiple processes---aggregators, splitters, relays \etc
%% \nv{

%% This is not necessarily the resulting parallelism achieved by \sys, which typically is above the level configured by the user.
%% This is because for each process (node in the graph), \sys creates multiple processes---aggregators, splitters, relays \etc
%% Some times the results give the impression of superlinear parallelism, but this has a simple explanation.
%% }
